Titeln på avhandlingens språk

### 2022-08-23 model.tex
writing

We begin by providing some formal definitions relating to step-based \acl{WCA}.
\begin{description}
    \item[Task:] understood as a finite sequence of instructions to be executed in order.
    \item[Step:] specific action to be performed by the user, described by a single instruction; e.g. put a green $1 \times 3$ brick on the board.
    \item[Step duration:] the time interval between 
    \item[Step execution time:]
    \item[Wait time:]
    \item[\ac{TTF}:]   
\end{description}

The step starts at \(t_0\), when the instruction is presented to the user.
We call the interval \(t_c - t_0\) the ``execution time'', corresponding to the time the user takes to complete the instruction.
The final sample of the step is taken at \(t_n\) and it takes \( t_{n+1} - t_n \) time units for the user to receive a reply from the backend (``last sample \ac{RTT}'').
Finally, we call the time interval between when the user finishes the instruction and the capturing of the final sample the ``wait time''; together with the last sample \ac{RTT} it composes the ``Time-to-Feedback'' of the step.%

\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{figs/task.png}
        \caption{%
            Overview of a task in a \ac{WCA}, composed of a series of steps.
            Each steps starts with an instruction being provided to the user and ends with the instruction for the next step.
            The \ac{WCA} continuously samples the task state, automatically triggering transitions between steps as correct (or incorrect) states are recognized.
        }\label{}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{figs/step_time.png}
        \caption{%
            Breakdown of a step into its timing components.
            The instruction for step \( M \) and \( M + 1 \) are provided to the user at \( t_0 \) and \( t_{n+1} \), respectively.
            \( t_k | k \in \{1, \ldots, n \} \) correspond to the \ac{WCA} sampling instants for step \( M \), and \( t_c \) marks the instant at which the user finishes performing the instruction.
        }\label{}
    \end{subfigure}
    \caption{}
\end{figure}

A task will be understood as a finite sequence of instructions to be performed in order. Step will refer to a specific action to be performed by the user, described by a single instruction; e.g. put a green 1 × 3 brick on the board (see Fig 2). A step starts with an instruction being given to the user, and ends when the assistant detects that the user has finished performing it. At that point, the assistant either provides a new instruction to the user, or the task ends.

\input{tables/empirical_exec_times.tex}

In our previous work~\cite{olguinmunoz:impact2021}, we identified four main results concerning the step execution times of humans in \ac{WCA}:

Based on these insights and the data collected for~\cite{olguinmunoz:impact2021}, we design a generator of realistic execution times for step-based \ac{WCA}.

>>>>

We begin by providing some definitions relating to step-based \acl{WCA}.
First of all, a \emph{step} is understood as a specific action to be performed by the user, described by a single instruction; a \emph{task} consists of a series of steps to be executed in sequence (see \cref{fig:task}).
More formally, a step starts when the corresponding instruction is provided to the user, and ends when the instruction for the next step is provided.
We call the time interval between these two events the \emph{step duration}.

Take \( \{ t_0, t_1, \ldots, t_{n + 1} \} \) a series of discrete and sequential sampling intervals at which the \ac{WCA} captures the state of the physical system --- see \cref{fig:step}.
\( t_0 \) corresponds to the instant at which the instruction for step \( M \) is provided and the first sample for said step is taken, and \( t_{n+1} \) to the instant at which the instruction for step \( M + 1 \) is provided.
Furthermore, \( t_c \) represents the instant at which the user finishes performing the instruction for step \( M \); the interval \( t_c - t_0 \) we call the \emph{execution time} of \( M \).
From the discrete sampling nature of the \ac{WCA} application, it follows that \( t_{n - 1} \leq t_c \leq t_{n} \); in plain English, the final state of the step is --- by definition --- always reached \emph{before} the final sample of the step is taken but after the next-to-last sampling instant.
We define the intervals \( t_n - t_c \) and \( t_{n + 1} - t_n \) as the \emph{wait time} and \emph{last sample \ac{RTT}}, respectively, for step \( M \).
The sum of these two values (i.e. the interval \( t_{n + 1} - t_c \)) we call \emph{time-to-feedback}.

\emph{Execution time} and \emph{time-to-feedback} correspond to the two key metrics necessary to characterize the interactions between system responsiveness and human behavior.

\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{figs/task.png}
        \caption{%
            Overview of a task in a \ac{WCA}, composed of a series of steps.
            Each steps starts with an instruction being provided to the user and ends with the instruction for the next step.
            The \ac{WCA} continuously samples the task state, automatically triggering transitions between steps as correct (or incorrect) states are recognized.
        }\label{fig:task}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{figs/step_time.png}
        \caption{%
            Breakdown of a step into its timing components.
            The instruction for step \( M \) and \( M + 1 \) are provided to the user at \( t_0 \) and \( t_{n+1} \), respectively.
            \( t_k | k \in \{1, \ldots, n \} \) correspond to the \ac{WCA} sampling instants for step \( M \), and \( t_c \) marks the instant at which the user finishes performing the instruction.
        }\label{fig:step}
    \end{subfigure}
    \caption{}
\end{figure}
